---
title: "p8105_hw5_xh2470"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

Import and clean the data.

```{r}
homicide_df = 
  read_csv("./p1_data/homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```

This data focused on homicides in 50 large U.S. cities.

Let's focus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()

```

Let's try to iterate across cities!

```{r}
#First off, write a function.

prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
      )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
      )
  
  return(city_test)
  
}


prop_test_function(baltimore_df)

homicide_df %>% 
  filter(city_state == "AlbuquerqueNM") %>% 
  prop_test_function()


```


```{r}
# iterate across all cities

results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data,prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

results_df

# another way of iteration
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  mutate(
    test_results = map2(unsolved, n, prop.test),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

```


Make a plot showing estimates and confidence intervals.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


# Problem 2

Create a tidy dataframe.

```{r}
# Create a dataframe containing all file names
df = 
  tibble(file = list.files(path = "./p2_data", full.names = TRUE))


# Iterate over file names and read in data for each subject 
read_data = function(x) {
  data = read_csv(x)
  }

df = 
  df %>% 
  mutate(data = purrr::map(file, read_data)) 

# Tidy the result
df = 
  df %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "Week",
    values_to = "Data") %>% 
  mutate(arm = substring(file,11,13),
         Arm = recode(arm, `con` = "Control", `exp` = "Experiment" ),
         Subject_ID = substring(file,15,16),
         Week = substring(Week,6,6)) %>% 
  select(-file,-arm) %>% 
  relocate(Arm, Subject_ID) 

df

```

Make a spaghetti plot.

```{r}

df %>% 
  mutate(Week = as.numeric(Week)) %>% 
  ggplot(aes(x = Week, y = Data, color = Subject_ID)) + 
  geom_point(alpha = .5) + 
  geom_line() +
  facet_grid(. ~ Arm) +
  labs(
    title = "Observation of each subject over time",
    x = "Week",
    y = "Observation"
  ) 
```

The plot shows that generally, subjects in the experiment group had higher observation than that of subjects in the control group. In the experiment group, observation increased with time. However, in the control group, the observation did not changed significantly over time, with a more stable trend compared with the experiment group.

# Problem 3

```{r}
# loads the iris dataset. 
set.seed(10)

iris_with_missing = 
  iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

# Write a function.
fill_in_missing = function(x) {
  
  if (is.numeric(x)) {
    x = replace_na(x, mean(x, na.rm = TRUE))
    }
  if (is.character(x)) {
    x = replace_na(x, "virginica")
    }
  
  return(x)
  
  }
  
# fill in missing values.
iris = 
  map(iris_with_missing, fill_in_missing) %>% 
  as_tibble()

iris 
```

